Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-24 RNARedPrint.tex
minor reformulation

Since $\F$ defines potentially more complex dependencies, which can
relate more than two positions, its dependencies cannot be similarily
represented by a graph. Instead, this requires a structure known as
\Def{hypergraph}, which consists of vertices (here, the sequence
positions) connected by \Def{hyperedges}, which are sets of
vertices. In this way, hypergraphs generalize undirected graphs, where
edges are sets of two vertices.
%Undirected graphs can be
%modeled as hypergraphs whose hyperedges are pairs of vertices, but
%hypergraphs also allow to express complex dependencies.

The set $\F$ of contributions induces the \Def{dependency
  (hyper)graph} $G_\F=(V, H)$ on sequence positions $V=\{1,\dots,n\}$
by interpreting the dependencies as hyperedges, i.e. $H =
\{\dep(f)\mid f\in \F\})$.

>>>>

Since $\F$ defines potentially more complex dependencies, which can
relate more than two positions, in general its dependencies cannot be 
represented by a graph. Instead, this requires a structure known as
\Def{hypergraph}, which consists of vertices (here, the sequence
positions) connected by \Def{hyperedges}, which are arbitrary sets of
vertices. In this way, hypergraphs generalize undirected graphs, where
each edge is a set of exactly two vertices.
%
The \Def{dependency (hyper)graph induced by $\F$} is then defined as the hypergraph $G_\F=(V, H)$ on sequence positions $V=\{1,\dots,n\}$
by interpreting the dependencies as hyperedges, i.e. $H =
\{\dep(f)\mid f\in \F\})$.
